Rising from the Ashes II: The Bar-driven Abundance Bimodality of the Milky Way

### 2025-02-18 paper/ms.tex
Update appendix figs

\section{Random Selection of Subhalos}\label{app:rand_fig1}
In Figures~\ref{fig:app0} to \ref{fig:app16}, we show a version of Figure~\ref{fig:fig1} but for a random selection of subhalos from our broader sample of 168 Milky Way-progenitors at $z=1.5$ in TNG50. It is from this sample that we selected our galaxy of interest. We first show this galaxy at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16. As discussed in the main text, three (172175, 178140, and 193025) display prominent bimodalities, indicating that bimodalities like the Milky Way's may not be uncommon in the entire simulation domain. All show more multimodal structure after the post-processing. The fact that bimodalities like in the main galaxy studied in this work (172175; Figure~\ref{fig:app0}) only appears in a few out of the 16 shown here indicates that the post-processing is not solely responsible for the bimodality.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_392276.pdf}
  \caption{The abundance plane made in a manner similar to Figure~\ref{fig:fig1}. We show }
  \label{fig:app0}
\end{figure*}

\figsetstart
\figsetnum{7}
\figsettitle{Abundance plane for a random subset of sample galaxies in this work.}
\figsetgrpstart
\figsetgrpnum{7.1}
\figsetgrptitle{Abundance plane for subhalo 392276.}
\figsetplot{app_172175.pdf}
\figsetgrpnote{Abundance plane for subhalo 392276.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.1}
\figsetgrptitle{Abundance plane for subhalo 172175.}
\figsetplot{app_172175.pdf}
\figsetgrpnote{Abundance plane for subhalo 172175.}
\figsetgrpend
\figsetend

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_2.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app1}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_10.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app2}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_143882.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app3}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_167392.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app4}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_289388.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app5}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_300903.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app6}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_348901.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app7}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_398784.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app8}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_404818.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app9}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_425719.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app10}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_439099.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app11}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_465255.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app12}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_494709.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app13}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_510273.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app14}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_547293.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app15}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_576516.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app16}
% \end{figure*}

>>>>

\section{Random Selection of Subhalos}\label{app:rand_fig1}
\edit1{In Figure~\ref{fig:app0}, we show the abundance plane of our fiducial galaxy at $z=0$. This reproduces the middle column of Figure~\ref{fig:fig1}. We also show the effect of our $\alpha$-enhancement procedure on this distribution when applied, from left to right, at redshifts of $1$, $1.5$, and $2$. (The $z=1.5$ column reproduces the right column of Figure~\ref{fig:fig1}). Qualitatively, the time at which the $\alpha$-enhancement is applied does not alter whether substructure arises in this plane. However, when it is applied at lower $z$, the peaks between modes do appear to be slightly further apart.}

\edit1{We show the same figure but with an additional random selection of 16 galaxies in the Milky Way-progenitor mass sample as a figure set (17 images), which is available in the online journal. Six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) display bimodalities, though none as prominent as the main galaxy studied in this work. Some substructure is present in many galaxies. In general, the $\alpha$-enhancement increases the strength of substructure in the abundance planes. The fact that bimodalities like in the main galaxy studied in this work do not universally appear in $\alpha$-enhanced galaxies indicates that the $\alpha$-enhancement is not solely responsible for the bimodality.}

\edit1{The timing of the $\alpha$-enhancement does not have a major effect on our fiducial galaxy (Figure~\ref{fig:app0}). However, for some (e.g., the green $\FeH=-0.25$ bin in 439099), structure arises only when the $\alpha$-enhancement is applied at sufficiently low redshift. We interpret this as the presence of some substructure inducing activity between $z=1$ and 2.}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_392276.pdf}
  \caption{\edit1{Abundance plane of the fiducial galaxy at $z=0$ and the effects of $\alpha$-enhancement applied at different redshifts. The leftmost panel shows the fiducial galaxy without enhancement, reproducing the middle column of Figure~\ref{fig:fig1}. The subsequent panels from left to right show the results of applying $\alpha$-enhancement at redshifts of 1, 1.5, and 2, respectively. The $z=1.5$ column reproduces the right column of Figure~\ref{fig:fig1}. The presence of substructure in the abundance plane is consistent across different application times of $\alpha$-enhancement, though applying it at lower redshifts appears to slightly increase the separation between modal peaks. This figure is part of a set of 17 images available in the online journal, showing similar plots for 16 additional galaxies from our Milky Way-progenitor mass sample. The varied responses to $\alpha$-enhancement across the sample, with only six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) displaying bimodalities, suggest that while $\alpha$-enhancement generally increases substructure, it is not solely responsible for creating bimodalities in abundance planes.}}
  \label{fig:app0}
\end{figure*}

\figsetstart
\figsetnum{7}
\figsettitle{Abundance plane for a random subset of galaxies in our Milky Way-progenitor mass sample, with and without $\alpha$-enhancement.}
\figsetgrpstart
\figsetgrpnum{7.1}
\figsetgrptitle{Subhalo 392276.}
\figsetplot{app_392276.pdf}
\figsetgrpnote{Abundance plane for subhalo 392276.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.2}
\figsetgrptitle{Subhalo 2.}
\figsetplot{app_2.pdf}
\figsetgrpnote{Abundance plane for subhalo 2.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.3}
\figsetgrptitle{Subhalo 10.}
\figsetplot{app_10.pdf}
\figsetgrpnote{Abundance plane for subhalo 10.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.4}
\figsetgrptitle{Subhalo 143882.}
\figsetplot{app_143882.pdf}
\figsetgrpnote{Abundance plane for subhalo 143882.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.5}
\figsetgrptitle{Subhalo 167392.}
\figsetplot{app_167392.pdf}
\figsetgrpnote{Abundance plane for subhalo 167392.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.6}
\figsetgrptitle{Subhalo 289388.}
\figsetplot{app_289388.pdf}
\figsetgrpnote{Abundance plane for subhalo 289388.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.7}
\figsetgrptitle{Subhalo 300903.}
\figsetplot{app_300903.pdf}
\figsetgrpnote{Abundance plane for subhalo 300903.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.8}
\figsetgrptitle{Subhalo 348901.}
\figsetplot{app_348901.pdf}
\figsetgrpnote{Abundance plane for subhalo 348901.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.9}
\figsetgrptitle{Subhalo 398784.}
\figsetplot{app_398784.pdf}
\figsetgrpnote{Abundance plane for subhalo 398784.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.10}
\figsetgrptitle{Subhalo 404818.}
\figsetplot{app_404818.pdf}
\figsetgrpnote{Abundance plane for subhalo 404818.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.11}
\figsetgrptitle{Subhalo 425719.}
\figsetplot{app_425719.pdf}
\figsetgrpnote{Abundance plane for subhalo 425719.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.12}
\figsetgrptitle{Subhalo 439099.}
\figsetplot{app_439099.pdf}
\figsetgrpnote{Abundance plane for subhalo 439099.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.13}
\figsetgrptitle{Subhalo 465255.}
\figsetplot{app_465255.pdf}
\figsetgrpnote{Abundance plane for subhalo 465255.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.14}
\figsetgrptitle{Subhalo 494709.}
\figsetplot{app_494709.pdf}
\figsetgrpnote{Abundance plane for subhalo 494709.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.15}
\figsetgrptitle{Subhalo 510273.}
\figsetplot{app_510273.pdf}
\figsetgrpnote{Abundance plane for subhalo 510273.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.16}
\figsetgrptitle{Subhalo 547293.}
\figsetplot{app_547293.pdf}
\figsetgrpnote{Abundance plane for subhalo 547293.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.17å}
\figsetgrptitle{Subhalo 576516.}
\figsetplot{app_576516.pdf}
\figsetgrpnote{Abundance plane for subhalo 576516.}
\figsetgrpend
\figsetend

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_2.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_10.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app2}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_143882.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_167392.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app4}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_289388.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app5}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_300903.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app6}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_348901.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app7}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_398784.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app8}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_404818.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app9}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_425719.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app10}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_439099.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app11}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_465255.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app12}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_494709.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app13}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_510273.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app14}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_547293.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app15}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_576516.pdf}
  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
  \label{fig:app16}
\end{figure*}
